### 2015-06-09 paper/paper.Rmd
started paragraph on the purpose of EDA

The vast majority of students spend less than 10 hours studying per week. The pattern  suggests decreasing benefits to increased out of school study time after 10 hours.

@@

# Summary

>>>>

The vast majority of students spend less than 10 hours studying per week. The pattern  suggests decreasing benefits to increased out of school study time after 10 hours. The thickness of the standard-error bars in the plot are an indication of the sample size.

@@

# Discussion

We have conducted what would be considered to be an exploratory analysis of the PISA data. There is a big difference between exploratory analyses and confirmatory analyses. When many people think of statistics they have in mind confirmatory methods, which involve deciding on a hypothesis, collecting the data, and doing a statistical test of significance. Exploratory data analysis is different, it focuses on the data at hand, and the goal is to let the data inform, to use various methods, primarily visual to find relationships and patterns and anomalies that may not have been anticipated ahead of the data collection. Exploratory analyses often lead to designed experiments where conditions are controlled, or specific data collection with all the controls to allow for hypothesis testing. Exploratory analysis is particularly important for today's big data society.
